---
title: "Untitled"
format: html
editor: visual
---
```{r}
here::i_am('test.Rproj')
```

## Variable

A variable is the name of a data manipulated by R

```{r}
mo <- 2.5
```

Three parts : 
1) 'mo' : name of the variable
2) <- : assignment operator
3) '2.5' : the value

```{python}
#| eval: false
#| include: false
mo = 2.5
```

Basic numeric operations

```{r}
12/4
```
Everywhere i would use a value, I can use instead a variable if the value of the variable is compatible with what is expected.
```{r}
mo*2
```

### Types

Values (and therefore variables) have types. A type specifies what values are possible (like integers versus real numbers) and what operations can be computed on the values.

- real numbers : '2,5', nombre écriture scientifique
- integers '135'
- logical values "TRUE" and "FALSE"
- strings (small texts)
- fonctions

### (almost) everything is a vector

i am declaring x as a variable with 4 values
```{r}
x <- c(-1, 1.5, 4, -123)
```

```{r}
x
```

```{r}
typeof(c)
```
all values to a vector are of the same type

```{r}
y <- c(1, 1.8)
y
typeof(y)
z <-c(1L, 2L)
typeof(z)

```

```{r}
world <- c("1", TRUE, 2.5, 1L)
typeof(world)
world
```
```{r}
length(world)
```

```{r}
world[1]
```
missing values : 
```{r}
world[5]
```
negative 
```{r}
world
world[-3]
```

### Class
```{r}
class(1.5)
```


```{r}
iris[1]
typeof(iris[1])
ckass(iris[1])
```


```{r}
iris[[1]]
```
single pair of barackets : keep the type, extract a subset of the content

```{r}
length(iris)
```
```{r}
library(ggplot2)

iris_petal_plot <- ggplot(iris, aes(x = Petal.Length, y = Petal.Width)) +
  geom_point()

print(iris_petal_plot)
```


